Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-07-13 template.tex
Updates from Overleaf

The imaginary part of $I$ is proportional to \textit{Dawson's integral, $D(x)$} \cite{NIST:DLMF}:

@@

Let $b = jq$, and $w(q)$ be the \textit{Faddeeva function} \cite{NIST:DLMF}.  The integral becomes

@@

\mathcal{E}_{r * s}(t) = \frac{1}{2} | r_a(t) * s_a(t) | \label{eq:final2}

@@

@@

As above, let $b=x+\frac{1}{2}z$, and $b = j q$.  In a procedure resembling the calculation for $r_a(t) * \Re\lbrace s_a(t)\rbrace$, the result for $I(x,z)$ is

@@

From the definition of $q$ and the chain rule, $dw(q)/dx = -jdw(q)/dq$, and $dw(q)/dq = -2qw(q)+2j/\sqrt{\pi}$ \cite{NIST:DLMF}.  The final result is left in terms of the real part of the Faddeeva function, which may be computed using the \textit{Voigt function} $U(x,t)$ \cite{NIST:DLMF,PhysRevD.105.123019}.
s * r = -\sqrt{\pi}R_0 E_0 \sigma_t^2 \\ \left(xe^{-x^2} \Re\left\lbrace w(q)\right\rbrace + j\frac{1}{2}e^{-x^2} \frac{d\Re\lbrace w(q)\rbrace}{dq} \right) \label{eq:final3}
\item To illustrate the accuracy and efficiency of the model, Eq. \ref{eq:final}-\ref{eq:final2} and \ref{eq:final3}, are shown in Fig. \ref{fig:fig1}.
\begin{figure}
\includegraphics[width=0.5\textwidth]{July3rd_plot1.pdf}
\includegraphics[width=0.5\textwidth]{July3rd_plot2.pdf}
\caption{\label{fig:fig1} (Top) The thin black line represents $s(t) * r(t)$.  The light gray envelope represents the envelope of $s(t) * r(t)$ computed with the Python3 package scipy.special.hilbert. The dark gray envelope represents Eq. \ref{eq:final}-\ref{eq:final2}. (Bottom) Same as top, for different parameter values.}

>>>>

The imaginary part of $I$ is proportional to \textit{Dawson's integral, $D(x)$:}

@@

Let $b = jq$, and $w(q)$ be the \textit{Faddeeva function}.  The integral becomes

@@

\mathcal{E}_{r * s}(t) = \frac{1}{2} | r_a(t) * s_a(t) |

@@

\item Two examples of comparisons of Eq. \ref{eq:final} to the convolution of $s(t)$ and $r(t)$ are given in Fig. \ref{fig:fig1} below.
\begin{figure}[hb]
\includegraphics[width=0.5\textwidth]{March12_plot1.pdf}
\includegraphics[width=0.5\textwidth]{March12_plot2.pdf}
\caption{\label{fig:fig1} (Top) The thin black line represents $s(t) * r(t)$.  The dark gray envelope represents the envelope of $s(t) * r(t)$ computed with the Python3 package scipy.special.hilbert. The light gray envelope represents Eq. \ref{eq:final}. (Bottom) Same as top, for different parameter values.}
\clearpage

@@

As above, let $b=x+\frac{1}{2}z$, and $b = j q$.  In a procedure resembling the calculation for $r_a(t) * \Re{s_a(t)}$, the result for $I(x,z)$ is

@@

Because the Faddeeva function is \textit{entire}, the derivative commutes with the $\Re\lbrace\rbrace$ operator.  From the definition of $q$ and the chain rule, $dw(q)/dx = -jdw(q)/dq$.  The complex derivative 
